---
title: "2018 Soybean Production and Dicamba Survey"
author: "Maxwel Coura Oliveira and Rodrigo Werle"
date: "11/9/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(tidyverse)
library(ggplot2)
library(knitr)
library(kableExtra)
```


# Demographics 

```{r include=FALSE}
WIdata=read.csv("2018SurveyWI.csv")
str(WIdata)
```


## Question 1

```{r}
WIdata %>% 
  filter(!is.na(County)) %>%
  count(County) 
```


## Question 2


```{r}
WIdata %>% 
  count(Role) 
```

## Question 3

Total soybean acres planted/managed in 

###2017
```{r Question32017}
WIdata %>% 
  filter(!is.na(SoyA17)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(SoyA17), minimum=min(SoyA17), maximum = max(SoyA17), sum=sum(SoyA17))
```
### 2018
```{r Question32018}
WIdata %>% 
  filter(!is.na(SoyA18)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(SoyA18), minimum=min(SoyA18), maximum = max(SoyA18), sum=sum(SoyA18))
```
### 2019
```{r Question32019}
WIdata %>% 
  filter(!is.na(SoyA19)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(SoyA19), minimum=min(SoyA19), maximum = max(SoyA19), sum=sum(SoyA19))
```


## Question 4

. Total Xtend soybean acres planted/managed in

### 2017
```{r Question42017}
WIdata %>% 
  filter(!is.na(XtendA17)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(XtendA17), minimum=min(XtendA17), maximum = max(XtendA17), sum=sum(XtendA17))
```

### 2018
```{r Question42018}
WIdata %>% 
  filter(!is.na(XtendA18)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(XtendA18), minimum=min(XtendA18), maximum = max(XtendA18), sum=sum(XtendA18))
```

### 2019
```{r Question42019}
WIdata %>% 
  filter(!is.na(XtendA19)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(XtendA19), minimum=min(XtendA19), maximum = max(XtendA19), sum=sum(XtendA19))
```


## Question 5

Total Xtend soybean acres sprayed with dicamba burndown (preplant or pre-emergence) in

### 2017
```{r Question52017}
WIdata %>% 
  filter(!is.na(DicambaPRE17)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(DicambaPRE17), minimum=min(DicambaPRE17), maximum = max(DicambaPRE17), sum=sum(DicambaPRE17))
```

### 2018
```{r Question52018}
WIdata %>% 
  filter(!is.na(DicambaPRE18)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(DicambaPRE18), minimum=min(DicambaPRE18), maximum = max(DicambaPRE18), sum=sum(DicambaPRE18))
```

### 2019
```{r Question52019}
WIdata %>% 
  filter(!is.na(DicambaPRE19)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(DicambaPRE19), minimum=min(DicambaPRE19), maximum = max(DicambaPRE19), sum=sum(DicambaPRE19))
```



## Question 6

Total Xtend soybean acres sprayed post-emergence with dicamba burdown in 

### 2017
```{r Question62017}
WIdata %>% 
  filter(!is.na(DicambaPOST17)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(DicambaPOST17), minimum=min(DicambaPOST17), maximum = max(DicambaPOST17), sum=sum(DicambaPOST17))
```

### 2018
```{r Question62018}
WIdata %>% 
  filter(!is.na(DicambaPOST18)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(DicambaPOST18), minimum=min(DicambaPOST18), maximum = max(DicambaPOST18), sum=sum(DicambaPOST18))
```

### 2019
```{r Question62019}
WIdata %>% 
  filter(!is.na(DicambaPOST19)) %>% 
  group_by(Role) %>% 
  summarise(n = n(), average = mean(DicambaPOST19), minimum=min(DicambaPOST19), maximum = max(DicambaPOST19), sum=sum(DicambaPOST19))
```


## Question 7

Do you own a sprayer/spray your herbicide programs?   

```{r Question7}
WIdata %>% 
  filter(!is.na(OwnSpr)) %>% 
  group_by(Role) %>% 
  count(OwnSpr)
```


## Question 8

At the start of the season, did you use an effective pre-emergence herbicide program with multiple effective sties of action before or at planting?

```{r Question8}
WIdata %>% 
  filter(!is.na(UsePRE)) %>% 
  group_by(Role) %>% 
  count(UsePRE)
```


```{r Question8followup}
WIdata %>% 
  filter(!is.na(UsePRE)) %>% #Need to update heading
  group_by(Role) %>% 
  count(UsePRE)
```

----------------------------------------------------------------------------------------------------------------------------------
# DICAMBA APPLICATION POST-EMERGENCE IN XTEND SOYBEAN 

## Question 9

Which dicamba formulation did you use in Xtend soybeans

```{r Question9}
WIdata %>% 
  filter(!is.na(DicamabaFormulation)) %>% 
  group_by(Role) %>% 
  count(DicamabaFormulation) 
```


## Question 11

Did you include a drift reduction agent (DRA) in the tank-mix

```{r Question11}
WIdata %>% 
  filter(!is.na(DrifRed)) %>% 
  group_by(Role) %>% 
  count(DrifRed) 
```


## Question 12

Did you include glyphosate in the tank-mix

```{r Question12}
WIdata %>% 
  filter(!is.na(IncludeGLY)) %>% 
  group_by(Role) %>% 
  count(IncludeGLY) 
```



## Question 13

Did you include post-emergence herbicides other than glyphosate in the tank-mix

```{r Question13}
WIdata %>% 
  filter(!is.na(IncludePOST)) %>% 
  group_by(Role) %>% 
  count(IncludePOST) 
```


## Question 14

Did you include soil-residual herbicides (Group 15) in the POST-emergence tank-mix   

```{r Question14}
WIdata %>% 
  filter(!is.na(IncludeG15)) %>% 
  group_by(Role) %>% 
  count(IncludeG15) 
```


## Question 15

Did dicamba application in your Xtend soybeans injured neighboring soybean fields?

```{r Question15}
WIdata %>% 
  filter(!is.na(DicambaInjuryNeigh)) %>% 
  group_by(Role) %>% 
  count(DicambaInjuryNeigh) 
```



## Question 16 

Has weed management in soybeans significantly improved with the adoption of Xtend soybean

```{r Question16}
WIdata %>% 
  filter(!is.na(ImpWeedC)) %>% 
  group_by(Role) %>% 
  count(ImpWeedC) 
```

----------------------------------------------------------------------------------------------------------------------------------

# NON-XTEND SOYBEAN ACRES

## Question 17 

Did you notice dicamba injury in your non-Xtend soybeans?

```{r Question17}
WIdata %>% 
  filter(!is.na(DicambaInjuryOwn)) %>% 
  group_by(Role) %>% 
  count(DicambaInjuryOwn) 
```


## Question 18 

Did you file an official complaint with the Department of Agriculture? 

```{r Question18}
WIdata %>% 
  filter(!is.na(FileComp)) %>% 
  group_by(Role) %>% 
  count(FileComp) 
```

## Question 19 # CHECK THIS ONE

What do you believe was (were) the main cause(s) for dicamba injury on your non-Xtend soybean?

```{r Question19}
WIdata %>% 
  unite(CausesInj, CouseDicambaInjury, CouseDicambaInjury1, CouseDicambaInjury2, CouseDicambaInjury3, CouseDicambaInjury4, CouseDicambaInjury5, CouseDicambaInjury6, CouseDicambaInjury7, CouseDicambaInjury8, sep= "", remove =TRUE) %>% 
  filter(!is.na(CausesInj)) %>% 
  group_by(Role) %>% 
  count(CausesInj) 
```


## Question 20 

Do you expect yield reduction in your dicamba injured soybean?

```{r Question20}
WIdata %>% 
  filter(!is.na(YieldRedSoyInjury)) %>% 
  group_by(Role) %>% 
  count(YieldRedSoyInjury) 
```


----------------------------------------------------------------------------------------------------------------------------------

## Question 21 

Do you think the technology should be available to producers next growing season?

```{r Question21}
WIdata %>% 
  filter(!is.na(KeepXtend)) %>% 
  group_by(Role) %>% 
  count(KeepXtend) 
```


## Question 22 

Any thoughts you would like to share regarding Xtend soybean

```{r Question22}
WIdata %>% 
  filter(!is.na(Comments)) %>% 
  group_by(Role) %>% 
  count(Comments) 
```
